
\section*{Acknowledgements}
We would like to thank the anonymous referee for constructive comments. M.R. and H.-J.S.~are supported by the U.S.~Department of Energy, Office of Science, Office of High Energy Physics under Award Number DE-SC0014329. This research used the Dark Energy Spectroscopic Instrument (DESI) allocation resources of the National Energy Research Scientific Computing Center (NERSC), a U.S. Department of Energy Office of Science User Facility operated under Contract No. DE-AC02-05CH11231. M.R. would like to thank Stephen Bailey, NERSC, and the DESI collaboration for providing computing resources to carry out the initial phases of this work; Anand Raichoor for providing the stellar mask and discussions on targetting; Nick Hand and Yu Feng for helping with Nbodykit and mock generations; Jeffrey Newman, Arnaud De-Mattia, and Marc Manera for discussions on machine learning and cross-validation; Ted Kisner, Rollin Thomas, and Joel Brownstein for helping with high-performance computing; Dustin Lang, John Moustakas, and Arjun Dey for discussions about the Legacy Surveys and data reduction pipelines. M.R. and H.J. would like to thank Patrick McDonald for discussions on window effects and error analyses. AJR is grateful for support from the Ohio State University Center for Cosmology and Particle Physics. We would like to appreciate the open-source software and modules that were invaluable to this research: HEALPix, Fitsio, Tensorflow, Scikit-Learn, NumPy, SciPy, Nbodykit, Pandas, IPython, Jupyter, GitHub.